%!TEX root = ../../common/main.tex

\section[
  head={\CP violation in decays of \BdToJpsiKS},
  tocentry={\CPHyperref violation in decays of \BdToJpsiKSHyperref}
]{\CPbfsf violation in decays of \BdToJpsiKSbfsf}
\label{sec:cpv_theory:bd2jpsiks}

The decay mode \BdToJpsiKS is well known [] as the gold-plated channel to measure
\CP violation in \Bd decays. With negligible contributions from \DCS
modes [], a $\ovE{\bquark}\to\ovE{\cquark}\cquark\ovE{\squark}$ transition
dominated by a single weak phase [], and an easy to reconstruct final state the
analysis of \BdToJpsiKS decays is a unique way to test the \SM quark flavour
sector.

\missing{Feynman diagram for \BdToJpsiKS}
\missing{Feynman diagram for both decay paths}

The decay is characterized by a $\Bd$ or $\Bdbar$ meson decaying into an
intermediate $\Jpsi$ and $\Kz$ meson. To take advantage of the superior
detection efficiency of charged particles the subsequent $\JpsiToMuMu$ decay
mode is chosen, as well as the decay of the $\Kz$ into two oppositely charged
pions. The decay $\KzToPiPi$ is mediated by the mass eigenstates $\KS$ and $\KL$
of the neutral kaon. Besides second-order effects discussed in
\cref{sec:measurement_of_sin2beta:cpv_measurement:kaon_regeneration}, the \CP
violating decay of the long lived eigenstate $\KL$ into two pions is neglected.
Thus, the two pion final state used in this analysis with an invariant mass that
matches the $\Kz$ mass, is denoted as a $\KS$. 

The $\mumu\pipi$ final state is common to both initial \Bmesons, hence can be
reached either directly or after mixing of the \Bmeson states and the decay time
dependent \CP asymmetry \CPAsymmetry can be defined using
\cref{eq:cpv_theory:flavour_physics:time_evolution:differential_decay_rates} as
%
\begin{equation}\label{eq:cpv_theory:bd2jpsiks:cp_asymmetry}
  \begin{split}
    \CPAsymmetry &\equiv 
      \frac{\Gamma\bigl(\decay{\Bdbar(\obsTime)}{\Jpsi\KS}\bigr) - \Gamma\bigl(\decay{\Bd(\obsTime)}{\Jpsi\KS}\bigr)}
           {\Gamma\bigl(\decay{\Bdbar(\obsTime)}{\Jpsi\KS}\bigr) + \Gamma\bigl(\decay{\Bd(\obsTime)}{\Jpsi\KS}\bigr)} \\
                 &= \frac{\SJpsiKS\sin(\DMd t) - \CJpsiKS\cos(\DMd t)}{\cosh\bigl(\frac{\DG t}{2}\bigr) + \DJpsiKS\sinh\bigl(\frac{\DG t}{2}\bigr)} \eqcm
  \end{split}
\end{equation}
%
where $\Bd$ and $\Bdbar$ denote the meson production flavour at $t=0$.

Considering a vanishing decay width difference of the two mass eigenstates
$\DGd/\Gd = \num{0.001 +- 0.010}$ \cite{Amhis:2014hma} the \CP asymmetry further
simplifies to
%
\begin{equation}
  \CPAsymmetry = \SJpsiKS\sin(\DMd t) - \CJpsiKS\cos(\DMd t) \eqpd
\end{equation}
%
The \CP coefficients introduced in
\cref{eq:cpv_theory:flavour_physics:time_evolution:cp_coefficients} can be
approximated to a high precision to be
%
\begin{equation}
  \CJpsiKS = 0 \eqand 
  \SJpsiKS = \sintwobeta \eqcm
\end{equation}
%
as direct \CP violation is expected to be small
$\vert\ovE{A}_{\Jpsi\KS}/A_{\Jpsi\KS}\vert\approx 1$ and \CP violation in mixing
is experimentally excluded ($\vert q/p \vert = 1$). Thus, eventually the \CP
asymmetry reduces to
%
\begin{equation}
  \CPAsymmetry = \sintwobeta\sin(\DMd t) \eqcm
\end{equation}
%
with $\beta$ being the one of the angles of the ${(\bquark,\dquark)}$ unitarity
triangle. 

The current world average of
%
\begin{equation}
  \sintwobeta = \num{0.679 +- 0.020}
\end{equation}
%
is mostly dominated by measurements by \Babar and \Belle in the \BdToJpsiKS
channel where both the $\elel$ and $\mumu$ final states of the $\Jpsi$ as well
as the $\pipi$ and $\piz\piz$ final states of the $\KS$ are studied. \Belle
\cite{Adachi:2012et} reports
%
\begin{equation*}
  \begin{split}
    \SJpsiKS^{\Belle} &= 0.670 \pm 0.029 \statp \pm 0.013 \systp \eqcm \\
    \CJpsiKS^{\Belle} &= 0.015 \pm 0.021 \statp \pm {}_{0.045}^{0.023} \systp \eqcm
  \end{split}
\end{equation*}
%
while the \Babar measurement \cite{Aubert:2009aw} yields
%
\begin{equation*}
  \begin{split}
    \SJpsiKS^{\Babar} &= 0.657 \pm 0.036 \statp \pm 0.012 \systp \eqcm \\
    \CJpsiKS^{\Babar} &= 0.026 \pm 0.025 \statp \pm 0.016 \systp \eqpd
  \end{split}
\end{equation*}
%
A first measurement of $\sintwobeta$ was performed by the \LHCb collaboration
using a data sample corresponding to an integrated luminosity of
$\SI{1}{\per\femtobarn}$ collected during \RunOne in 2011. The analysis
comprised $\num{8000}$ flavour-tagged \BdToJpsiKS candidates, reconstructed in
the $\mumu\pipi$ final state. The reported results are
%
\begin{equation*}
  \begin{split}
    \SJpsiKS &= 0.73 \pm 0.07 \statp \pm 0.04 \systp \eqcm \\
    \CJpsiKS &= 0.03 \pm 0.09 \statp \pm 0.01 \systp \eqpd
  \end{split}
\end{equation*}
%
















